Quantifying social distancing behaviour across Australia in response to COVID-19

### 2020-04-19 manuscript/ms.Rmd
expand on the behavioural probability distribution stuff

  For each latent behaviour $k$, these parameters describe the behavioural reponse to each event via a logistic distribution. Where the behaviour occurs at a single point in time, these parameters give rise to a logistic distribution over the times at which members of the population exhibit this behaviour, where the fraction of the population exhibiting behaviour $k$ in response to event $j$ at time $t$ is given by the probability density function of the logistic distribution:

$$
p_{j,k}(t) = \frac{e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}{\kappa_{j,k} (1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}) ^ 2}
$$

  Where the latent behavioural state is described by individuals switching from one behavioural state to another, the fraction of the population that have made the switch by time $t$ is given by the cumulative density function of the logistic distribution:

$$
p_{j,k}(t) = \frac{1}{1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}
$$

  Since the latent factors are scaled between 0 and 1, we scale these probabilities such that their maximum value is the relative event impact parameter $\epsilon_{j,k}$, and the sum over these parameeters is constrained to 1. Therefore, where the behaviour is a function of only a single event, $\epsilon_{j,k}$ is fixed at 1. The contribution of each event to the behaviour is therefore given by:

<!-- MAKE THIS HAVE DENSITY EPSILON AT THE MEAN -->
<!-- HAS DENSITY 1/(4 * kappa) AT MEAN -->
<!-- SO DIVIDE BY THAT AND MULTIPLY BY EPSILON -->
<!-- MUTIPLY BY epsilon * 4 * kappa -->

<!-- CHECK THIS! -->
$$
f_{j,k}(t) = 4 \kappa_{j,k} \epsilon_{j,k} \frac{e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}{\kappa_{j,k} (1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}) ^ 2}
$$
And the cumulative contribution by:

$$
f_{j,k}(t) = \frac{\epsilon_{j,k}}{1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}
$$

>>>>

  For each latent behaviour $k$, these parameters describe the behavioural reponse to each event via a rescaled logistic probability distribution, with distribution location parameter $\tau_{j,k}$ and scale parameter $\kappa_{j,k}$, and a rescaling factor $\epsilon_{j,k}$. This logistic probability distribution can be used in two ways useful for modelling behaviour related to COVID-19. For behaviours that individuals enact at a specific point in time - such as increased grocery shopping, or travelling to a particular residence in preparation for social distancing - the probability density function gives the fraction of the population that enacts these behaviours at a given time. For behavioural states that individuals 'switch' to enacting at some point in time - such as increased social distancing behaviour - the cumulative density function gives the fraction of the population that have switched to this new behavioural state by a given time.

  These probabilities are then rescaled such that their maximum value is the relative event impact parameter $\epsilon_{j,k}$. This parameter is proportional to the fraction of the population that enacts a behaviour $k$ in response to event $j$. However, the data streams considered only provide information on *relative* behavioural changes among a subset of the population, there is therefore no information against which to calibrate an estimate of the *absolute* fraction of the population enacting a behaviour. Parameters $\epsilon_{j,k}$ are therefore constrained so that their sum over all events for a given behaviour is equal to 1; if only a single event is considered, $\epsilon_{j,k}$ is fixed at 1. The contribution of each event $j$ to an episodic behaviour is therefore given by:

$$
f_{j,k}(t) = 4 \epsilon_{j,k} \frac{e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}{(1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}) ^ 2}
$$

and the contribution to a state-switching behaviour is given by:

$$
g_{j,k}(t) = \frac{\epsilon_{j,k}}{1 + e^{-(t - \tau_{j,k}) / \kappa_{j,k}}}
$$
